---
title: "Validation"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F,message = F)
```

```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)
```

```{r}
fil<-list.files("/Users/Ben/DeepMeerkat/DeepMeerkat_20180301_145641",pattern="annotations.csv",recursive = T,full.names=T)

myread<-function(x){
  f<-read.csv(x)
  f$Video<-str_match(x,"DeepMeerkat_20180301_145641/(\\w+)/annotations.csv")[,2]
  return(f)
}


dat<-bind_rows(lapply(fil,myread))
dat<-dat %>% select(Frame,x,y,h,w,label,score,Video)
```

```{r}
#Write ground truth to file, it will be useful in the future. make sure there isn't duplicates

truth<-read.csv("/Users/Ben/Dropbox/DeepLearning/GroundTruth.csv")

#Missing frames
missing<-dat %>% anti_join(truth)%>% arrange(Video,Frame) %>% select(Video,Frame) %>% group_by(Video,Frame) %>% distinct()
head(missing)
write.csv(missing,"MissingGroundTruth.csv",row.names = F)
dat<-merge(dat,truth,by=c("Video","Frame")) 

#If multiple, choose Positive

sortpos<-function(d){
  if(length(unique(d$label))==2){
    d<-d %>% filter(label=="Positive")
  }
  return(d)
}
dat<-dat %>% group_by(Video,Frame) %>% do(sortpos(.))
dat<-dat %>% group_by(Video,Frame,label) %>% distinct(Video,Frame,.keep_all=TRUE)

dat %>% group_by(Video,Frame) %>% summarize(n=n()) %>% filter(n>1)

```

# General Statistics

How many videos?

```{r}
length(fil)
```

How many frames returned by video?
```{r}
dat %>% group_by(Video) %>% summarize(n=n()) %>% arrange(desc(n)) %>% as.data.frame()
```

How many hummimgbird frames?

```{r}
dat %>% filter(Truth=="Positive") %>% nrow()
```

# MotionMeerkat

What percentage of frames were returned? Each video is 21,600 frames long.

```{r}
dat %>% group_by(Video) %>% summarize(n=n()/21600 * 100) %>% arrange(desc(n))

returned<-dat %>% group_by(Video) %>% summarize(n=n()/21600 * 100) %>% arrange(desc(n))
returned
mean(returned$n)
sd(returned$n)
```

What percentage of returned frames had hummingbirds?

## Precision
Overall?

```{r}
prec<-function(MM){MM[MM$Truth=="Positive","n"]/(MM[MM$Truth=="Positive","n"] + MM[MM$Truth=="Negative","n"]) * 100}

MM<-dat %>% group_by(Video,Truth) %>% summarize(n=n()) %>% group_by(Video) %>% spread(Truth,n,fill = 0) %>% group_by(Video) %>% summarize(prec=Positive/(Negative + Positive) * 100) %>% mutate(prec=round(prec,3))
MM
mean(MM$prec)
sd(MM$prec)
```

# DeepMeerkat

## Overall

```{r}
DM<-dat %>% group_by(Truth,label) %>% summarize(n=n()) %>% mutate(newkey=paste(Truth,label,sep="_")) %>% ungroup() %>% select(-Truth,-label) %>% spread(newkey,n,fill=0) %>% summarize(TNR=Negative_Negative/(Negative_Negative + Negative_Positive),recall=Positive_Positive/(Positive_Positive + Positive_Negative),precision=Positive_Positive/(Positive_Positive+Negative_Positive)) %>% mutate(TNR=round(TNR,3)*100,precision=round(precision,3)*100,recall=round(recall,3)*100)
DM
```

## Per Video

```{r}
DM<-dat %>% group_by(Video,Truth,label) %>% summarize(n=n()) %>% mutate(newkey=paste(Truth,label,sep="_")) %>% ungroup() %>% select(-Truth,-label) %>% spread(newkey,n,fill=0) %>% group_by(Video) %>% summarize(TNR=Negative_Negative/(Negative_Negative + Negative_Positive),recall=Positive_Positive/(Positive_Positive + Positive_Negative),precision=Positive_Positive/(Positive_Positive+Negative_Positive)) %>% mutate(TNR=round(TNR,3)*100,precision=round(precision,3)*100,recall=round(recall,3)*100)
data.frame(DM)
mean(DM$TNR)
mean(DM$recall,na.rm=TRUE)
mean(DM$precision,na.rm=TRUE)
```

## Events captured?

How many missing frames were within 5 seconds of a positive event? These are the true missed data

```{r}
findClosest<-function(x){
  #distance to closest positive
  x<-x %>% filter(Truth=="Positive")
  closest<-sapply(x$Frame,function(y){
    mn<-min(abs(x$Frame[!x$Frame==y]-y)) 

    if(length(mn)==0){
      return(NA)
    } else{
      mn
    }
    })
  return(data.frame(x,closest))
}

dat %>% group_by(Video) %>% do(findClosest(.)) %>% arrange(Video,Frame) %>% filter(label=="Negative",Truth=="Positive") %>% filter(closest > 5)
```

#Tradeoffs

```{r}
dat$Binary<-NULL
dat$Binary[dat$label=="Positive"]<-dat$score[dat$label=="Positive"]
dat$Binary[dat$label=="Negative"]<-1-dat$score[dat$label=="Negative"]

gen_dat<-function(threshold){
  newdat<-dat %>% select(-label) %>% mutate(new_label=Binary>threshold) 
  newdat$new_label<-as.factor(newdat$new_label)
  levels(newdat$new_label)<-c("Negative","Positive")
  
  out<-newdat %>% group_by(Truth,new_label) %>% summarize(n=n()) %>% mutate(newkey=paste(Truth,new_label,sep="_")) %>% ungroup() %>% select(-Truth,-new_label) %>% spread(newkey,n,fill=0) %>% summarize(TNR=Negative_Negative/(Negative_Negative + Negative_Positive),recall=Positive_Positive/(Positive_Positive + Positive_Negative),precision=Positive_Positive/(Positive_Positive+Negative_Positive)) %>% mutate(TNR=round(TNR,3)*100,precision=round(precision,3)*100,recall=round(recall,3)*100) %>% mutate(Threshold=threshold)
  return(out)
}

threshdat<-lapply(seq(0.05,0.95,.05),gen_dat)
threshdat<-bind_rows(threshdat)
ggplot(threshdat,aes(x=Threshold)) + geom_point(aes(y=recall))  + geom_line(aes(y=TNR),col="red") + geom_point(aes(y=TNR),col="red") + geom_line(aes(y=recall)) + labs(y="Recall %",x="Acceptance Value") + theme_bw()
ggsave("Figures/Tradeoff.jpg",height=4,width=7)
dat %>% group_by(Truth) %>% summarize(n=n()) %>% mutate(n/sum(n))
```

```{r}
threshdat
```

How many total frames were returned

```{r}
filp<-list.files("/Users/Ben/DeepMeerkat/DeepMeerkat_20180301_145641",pattern="parameters.csv",recursive = T,full.names=T)

readp<-function(x){
  f<-read.csv(x,header=F)
  colnames(f)<-c("par","value")
  out<-data.frame(f,Video=str_match(x,"(\\w+)/parameters.csv")[,2])
  return(out)
}
parfiles<-bind_rows(lapply(filp,readp))

options(scipen = 999)
parfiles %>% group_by(par) %>% summarize(mean=mean(as.numeric(value))) 

```
